%-------------------------
% Resume in Latex
% Author : Gabriel Ong
% Website: https://www.overleaf.com/project
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/gongahkia}{\Large Gabriel Ong}} & Email : \href{mailto:gabrielzmong@gmail.com}{gabrielzmong@gmail.com}\\
  \href{https://gongahkia.github.io/}{gongahkia.github.io} & Mobile : +65-8123-9863 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Singapore Management University}{Singapore}
      {Bachelor of Science in Computing and Law;  GPA: 3.42}{Aug. 2023 -- Aug. 2026}
  \resumeSubHeadingListEnd

%-----------AWARDS---------------------
\section{Awards}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SMU Global Impact Scholarship Award}{Singapore}
      {Premier flagship scholars’ award}{Aug. 2023 -- Aug. 2026}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Yap.com}{Singapore}
      {Co-founder and Tech Development Head}{Jan 2024 - Present}
      \resumeItemListStart
        \resumeItem{FlutterFlow}
          {Adopted No-code framework to rapidly push out MVP for market valuation.}
        \resumeItem{Flutter}
          {Used Flutter SDK to develop and deploy multiple iterations of the Yap.com website and mobile app.}
        \resumeItem{Figma}
          {Storyboarding, prototyping and ideation with Figma and FigJam.}
      \resumeItemListEnd

    \resumeSubheading
      {SMU Legal Innovation and Technology (LIT)}{Singapore}
      {Tech Development Director}{Aug 2023 - Aug 2024}
      \resumeItemListStart
        \resumeItem{Software development}
          {Authored and Coauthored multiple open-source projects simplifying lawyering for Law students.}
        \resumeItem{Svelte Netlify}
          {Updated and deployed LIT website per modern UI/UX design philosophies and web frameworks.}
          \resumeItem{AWS Lambda}
          {Upgraded and sustained infra for LIT's LawTech day and the Annual Hackathon.}
      \resumeItemListEnd

\resumeSubheading
      {Tong Eng Group}{Singapore}
      {Property Development Intern}{Nov 2018 - Dec 2018}
      \resumeItemListStart
        \resumeItem{Microsoft 365 Suite}
          {Leveraged Microsoft Excel, Word and Powerpoint to sterilize data, compile summary analysis, and produce pitch decks of findings.}
        \resumeItem{Legal administration}
          {Assisted processing of legal documents for handover of properties.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{DC4U}
      {Drafts legal charges by transpiling a human-readable markup language to multiple target formats.}
    \resumeSubItem{Judgeman}
      {Browser extension that parses and formats Elitigation cases for readability.}
    \resumeSubItem{Skill Hunter}
      {Browser extension that optimizes SSO legislation for absorption by sanitising legalese.}
    \resumeSubItem{Gitfetch}
      {Grabs snapshots of Github profiles in the CLI.}
    \resumeSubItem{Ooe}
      {Toy markup language that transpiles to HTML.}
    \resumeSubItem{Wooden Tiger}
      {Performance, distance and score logging for golf games all within the browser.}
    \resumeSubItem{Shed}
      {Bare-bones, keyboard-only modal text editor.}
    \resumeSubItem{Kelp}
      {Complete productivity guru in the CLI.}
    \resumeSubItem{Thoth}
      {Comprehensive library of helpers for math and graphics rendering adhering to functional paradigms.}
    \resumeSubItem{Tikrit}
      {2D horror roguelike from a single Lua file.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \resumeSubItem{Languages}
      {Python, Javascript, Typescript, PHP, SQL, Ruby, Dart, Java, Rust, Lua}
   \resumeSubItem{Technologies}
      {Svelte, Flutter, Express, Ruby on Rails, Laravel, Tauri}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
